A Formal Model of Checked C

### 2023-01-10 sandp23/formal.tex
Adding all
[review] function pointer

\emph{\mzr{Rejecting}\mzs{Disallowing} unsafe types.}
The well-formed requirements of these types are presented in~\fig{fig:wftypesandbounds} (Appendix).
% 
These requirements \mzs{add additional restrictions for type creation and restrict the creation of unsafe types.}
\mzr{prevents unsafe types from being constructed}.
% 
\mzr{
  % 
  Consider the type ~\code{_t_Array_ptr<_Ptr<int>>} which describes a tainted
  array of checked pointers.
  % 
  Syntactically valid, this type is however \emph{illegal} in~\lang{} and
  rejected by the well-formedness requirement. 
}
% 
\mz{Made some changes to shift the emphasis in hope of improving clearness.}
% 
However, we can have a checked array whose elements are tainted pointers\mzs{,}\mzr{:}~\eg~\code{_t_Array_ptr<_t_Ptr<int>>} is a valid type.
%

% 
Function types are represented using a dependent function declarations,~\ie $\tfun{\overline{x}}{\overline{\tau}}{\tau}$,
where $\overline{x}$ represents a list of \tint{} type variables that bind bound variables appearing in $\overline{\tau}$ and $\tau$.
An example of a function pointer type is shown below:
\[\hspace*{-0.5em}
\begin{array}{l}
$\code{_t_ptr<(int)(_t_NT_Array_ptr<}$\tau$\code{> : count(}$n$\code{),}$\\
\qquad\qquad$\code{_NT_Array_ptr<}$\tau$\code{>: count(}$n$\code{))>}$
\\[0.2em]
\Leftrightarrow\;\; $\tptr{(\tfun{n}{ \tntarrayptr{0}{n}{\tau}{\tmode} \times \tntarrayptr{0}{n}{\tau}{\tmode}}{\tint})}{\tmode}$
\end{array}
\]
The function type also has well-formed requirements (\fig{fig:wffunctions} in Appendix), which disallows nesting checked or unchecked pointers inside tainted pointers.
Furthermore, these requirements also ensure that all variables in $\overline{\tau}$ and $\tau$ are bounded by $\overline{x}$.
\aravind{The syntax of well-formed requirements for functions is incorrect. It looks like the forall qualifier is missing.}

>>>>

\emph{\mzr{Rejecting}\mzs{Disallowing} unsafe types.}
The well-formed requirements of these types are presented in~\fig{fig:wftypesandbounds} (Appendix).
% 
These requirements \mzs{add additional restrictions for type creation and restrict the creation of unsafe types.}
\mzr{prevents unsafe types from being constructed}.
% 
\mzr{
  % 
  Consider the type ~\code{_t_Array_ptr<_Ptr<int>>} which describes a tainted
  array of checked pointers.
  % 
  Syntactically valid, this type is however \emph{illegal} in~\lang{} and
  is rejected by the well-formedness requirement. 
}
% 
\mz{Made some changes to shift the emphasis in hope of improving clearness.}
% 
However, we can have a checked array whose elements are tainted pointers\mzs{,}\mzr{:}~\eg~\code{_t_Array_ptr<_t_Ptr<int>>} is a valid type.
%

% 
Function types are represented using a dependent function declarations,~\ie $\tfun{\overline{x}}{\overline{\tau}}{\tau}$,
where $\overline{x}$ represents a list of \tint{} type variables that bind \mzu{bound}\mz{free?} variables appearing in $\overline{\tau}$ and $\tau$.
An example of a function pointer type is shown below:
\[\hspace*{-0.5em}
\begin{array}{l}
$\code{_t_ptr<(int)(_t_NT_Array_ptr<}$\tau$\code{> : count(}$n$\code{),}$\\
\qquad\qquad$\code{_NT_Array_ptr<}$\tau$\code{>: count(}$n$\code{))>}$
\\[0.2em]
\Leftrightarrow\;\; $\tptr{(\tfun{n}{ \tntarrayptr{0}{n}{\tau}{\tmode} \times \tntarrayptr{0}{n}{\tau}{\tmode}}{\tint})}{\tmode}$
\end{array}
\]
The function type also has well-formed requirements (\fig{fig:wffunctions} in Appendix), which disallows nesting checked or unchecked pointers inside tainted pointers.
Furthermore, these requirements also ensure that all variables in $\overline{\tau}$ and $\tau$ are bounded by $\overline{x}$.
\aravind{The syntax of well-formed requirements for functions is incorrect. It looks like the forall qualifier is missing.}
